A Hybrid Approach for News Recommender System using Optimization Methods

### 2021-05-27 paper/paper.tex
upd paper

        \begin{itemize}
            \item \Cref{sec:related} describes the relevant related work
            \item \Cref{sec:overview} contains overview of our approch
            \item \Cref{sec:input} describes input data
            \item \Cref{sec:approach} explains our modular design and architecture
            % \item \Cref{sec:implementation} describes the implementation of the algorithms in a real system
            \item \Cref{sec:evaluation} provides tests and experiments validating
our system’s results
            \item \Cref{sec:summary} presents conclusions
        \end{itemize}

@@

@@

\begin{equation}
    \texttt{user\_vector} \mathrel{+}= \texttt{action\_score} * \texttt{item\_vector}
\end{equation}

@@

Where action score is taken from table:

\begin{table}[h]
    \centering
    \begin{tabular}{cc}
        \toprule
        \textit{action} & \textit{score} \\
        \midrule
        shown but now viewed & -1 \\
        viewed & 0.5 \\
        emoji or comment & 0.5 \\
        read till the end & 1 \\
        \bottomrule
    \end{tabular}%
    \caption{actions' scores}
    \label{tab:action_score}
\end{table}

@@

\begin{equation}
    r_i = 1 - \cos{(\texttt{user\_vector}, \texttt{item\_vector})}
\end{equation}

@@

@@

@@

    So having all of this information allows us to tune the impact weight of each recommender using grid search.

>>>>

        \begin{itemize}
            \item \Cref{sec:related} describes the relevant related work
            \item \Cref{sec:overview} contains overview of our approch
            \item \Cref{sec:input} describes input data
            \item \Cref{sec:approach} explains our modular design and architecture
            % \item \Cref{sec:implementation} describes the implementation of the algorithms in a real system
            \item \Cref{sec:evaluation} provides tests and experiments validating
our system’s results
            \item \Cref{sec:summary} presents conclusions

        \end{itemize}

@@

We have actions while user interacts with the system and weights for items for each interaction (\cref{tab:action_score}).

\begin{table}[h]
    \centering
    \begin{tabular}{cc}
        \toprule
        \textit{action} & \textit{score} \\
        \midrule
        shown & -1 \\
        viewed & 2 \\
        emoji or comment & 1 \\
        read till the end & 1 \\
        \bottomrule
    \end{tabular}%
    \caption{actions' values}
    \label{tab:action_score}
\end{table}

All data is aggregated and each news item have an action score depending on what user had done with it. For instance, suppose user had viewed and item and left an emoji. Total score will be: $-1$ (user was shown an item) $+2$ (user viewed an item) $+1$ (user left an emoji) $=2$.

@@

\begin{equation}
    u_i = \sum_{j=1}^{n} v_j \times s_j
\end{equation}

\begin{itemize}
    \item $u_i$ -- vector of $user_i$
    \item $v_j$ -- vector of $item_j$
    \item $s_j$ -- action value of $item_j$
\end{itemize}

@@

@@

\begin{equation}
    r_{ui}=\cos (\theta)=\frac{\mathbf{u} \cdot \mathbf{v}}{\|\mathbf{u}\|\|\mathbf{v}\|}=\frac{\sum_{i=1}^{n} u_{i} v_{i}}{\sqrt{\sum_{i=1}^{n} u_{i}^{2}} \sqrt{\sum_{i=1}^{n} v_{i}^{2}}}
\end{equation}

\begin{itemize}
    \item $r_{ui}$ -- rating from $user$ to $item$
    \item $u$ -- vector of $user$
    \item $v$ -- vector of $item$
\end{itemize}

@@

\subsection{Combining}

    So having all of this information allows us to tune the impact weight of each recommender using grid search. So we are optimizing weight that are making impact at each recommender.

    The metric we are optimizing is MAP@20 that stands for Mean Average Precision.

@@

\subsection{Overview}

@@

\subsection{Metrics}

We are using three metrics to measure the quality of our recommenders:

    \begin{itemize}
        \item RMSE
        \item NDCG
        \item MAP@20
    \end{itemize}
